LAGOS lake depth

### 2020-11-25 tables/02_model_metrics.Rmd
generate alt metrics model table

>>>>

```{r 02_alternate_metrics, eval=TRUE}

dt_metrics <- read.csv("../data/01_depth_model/alternatives_metrics.csv",
                       stringsAsFactors = FALSE) %>%
  mutate_if(is.numeric, function(x) as.character(round(x, 2))) %>%
  mutate(proxy_proxy_rmse = paste0(
    round(as.numeric(proxy_proxy_rmse), 1), " m")) %>%
  mutate(proxy_proxy_rsq = round(as.numeric(proxy_proxy_rsq), 2)) %>%
  mutate(proxy_proxy_mape = paste0(
    round(as.numeric(proxy_proxy_mape), 0), " %")) %>%
  mutate(inlake_slope = gsub("inlake_", "", inlake_slope)) %>%
  mutate(nearshore_slope = gsub("nearshore_", "", nearshore_slope)) %>%
  arrange(proxy_proxy_rmse) %>%
  setNames(c("Inlake slope", "Nearshore slope", 
             "Inlake distance", "RMSE", "$R^2$", "MAPE"))

dt_metrics[2,] <- paste0("**", dt_metrics[2,], "**") # highlight row from main text
clipr::write_clip(
  gsub("%\\*\\*", "\\\\%\\*\\*",
  gsub("_", "\\\\_",
  gsub("%\\\\", "\\\\%\\\\",
  sub("\\\\midrule", "\\\\hline",
  sub("\\\\bottomrule", "\\\\hline",
  sub("\\\\toprule", "\\\\hline",
      knitr::kable(dt_metrics, digits = 2, format = "latex",
     booktabs = TRUE, linesep = "", align = c("lllllc"), escape = FALSE)))))))
   )
```
